\hspace*{10ex} Planning aircraft maintenances for the French Airforce

### 2018-10-30 latex/AFIS2018/poster_FP.tex
changes to poster and added resume for AFIS 2018

		\begin{tikzpicture}[remember picture,overlay] 
			\node [shift={(35 cm,5cm)}] at (current page.south west) {\includegraphics[height=8cm]{img/AFIS_logo_2.jpg}};
		\end{tikzpicture}

@@

	\begin{column}{\twocolwid}
			\vspace*{-5ex}
			\begin{alertblock}{}				
				\begin{itemize}
					\item Doctorant (email): Franco Peschiera (franco.peschiera@isae-supaero.fr)
					\item Directeurs de Thèse: Olga Battaïa, Alain Haït, Nicolas Dupin
					\item Laboratoire, Université: ISAE-SUPAERO
					\item Collaboration industrielle: DGA
				\end{itemize}
			\end{alertblock}

>>>>

		\begin{tikzpicture}[remember picture,overlay] 
			\node [shift={(38 cm,5cm)}] at (current page.south west) {\includegraphics[height=8cm]{img/AFIS_logo_2.jpg}};
		\end{tikzpicture}

@@

	\begin{column}{\twocolwid}
			\vspace*{-6ex}
			\begin{alertblock}{}				
				\begin{itemize}
					\item Franco Peschiera (franco.peschiera@isae-supaero.fr)
					\item Directeurs de Thèse: Olga Battaïa, Alain Haït, Nicolas Dupin
					\item Institut: ISAE-SUPAERO
					\item Collaboration industrielle: DGA
				\end{itemize}
			\end{alertblock}
